### 2016-08-01 hoist.tex
formatting. NFC
restructuring

Of course, a sinking optimization could just sink the computation of both tmax and tmin, and since the final operation is an addition (aasociative under fast math), the entire if-else
code would go away.

@@

\section{Hoisting scalars}
Scalars are the easiest to hoist because we do not have to analyze for mem-refs. As long as all the
operands are available (which in SSA form we do, or may be there are chained dependencies), the scalar can
be hoisted. Care must be taken in case of hoisting scalars too far, as that may increase register pressure
and result in spills. For example hoisting a scalar past a call. In that case the call may result in
save and restore of the register the scalar may be defined to. In our current implementation
we do not hoist scalars past a call. Another way to mitigate this problem is be to
reinstantiate (rematerialize) the computation after a call (may be as a different pass).

\section{Hoisting calls}
Calls can be hoisted by value-numbering all the arguments. For safety we have to check that no other side-effects are there
between call and the hoisting point, just like loads and stores.

@@

@@

In the case when more than one computation from the same basic block shows up as redundant.
e.g.
BB1
load a;
....
store .;
....
load a;

>>>>

Of course, a sinking optimization could just sink the computation of
both tmax and tmin, and since the final operation is an addition
(asociative under fast math), the entire if-else code would go away.

@@

\section{Hoisting scalars}
Scalars are the easiest to hoist because we do not have to analyze
them for aliasing memory references. As long as all the operands are
available (which in SSA form we do, or may be there are chained
dependencies), the scalar can be hoisted. Care must be taken in case
of hoisting scalars too far, as that may increase register pressure
and result in spills. For example hoisting a scalar past a call. In
that case the call may result in save and restore of the register the
scalar may be defined to. In our current implementation we do not
hoist scalars past a call. Another way to mitigate this problem is be
to reinstantiate (rematerialize) the computation after a call (may be
as a different pass).

@@

\section{Hoisting calls}
Calls can be hoisted by value-numbering all the arguments. For safety
we have to check that there are no other side-effects between a call and
its hoisting point, just like loads and stores.

@@

In the case when more than one computation from the same basic block
shows up as redundant.

e.g.
BB1
load a;
....
store .;
....
load a;
